---
title: Survey fungicide sensitivity of S. sclerotiorum from drybean and soybean from
  the U.S.
output:
  html_document:
    df_print: paged
  pdf_document: default
---

 

```{r set packages, warning= FALSE, include=FALSE}
library(tidyverse)
library(ggplot2)
library(ezec)
#library(NRES803)
library(broom)
library(ggridges)
library(cowplot)
library(gridExtra)
library(kableExtra)
library(arsenal)
library(DescTools)
library(knitr)
library(agricolae)



```

#  Background   

Knowledge of baseline sensitivity of a pathogen population to fungicides is important for detection of resistance and for achieving effective disease management strategies (Brent and Holloman 2007). QoI, DMI, MBC and SDHI fungicides are used to control _S. sclerotiorum_ in an IPM approach in soybean and dry bean in the U.S. DMI fungicides are considered to medium risk of resistance emergence, whereas QoI, SDHI and MBC are high risk (Fungicide Resistance Action Committee 2016). MBC and dicarboximide fungicides are used for white mold in Brazil, wherein resistance to MBC fungicide, Thiophanate methyl, has been reported (Lehner et al. 2015). Fungicide resistance has also been reported in China to the MBC, Carbendazim and dicarboximide, Dimethachlon (Ma et al. 2009).

COMMONLY USED FUNGICIDES FOR WM .

Thiophanate methyl (MBC) fair control; launched 1970
Tetraconazole (DMI)  fair control; launched 1988
Picoxystrobin (QoI) good-very good control; launched 2000
Boscalid (SDHI) very good control; launched 2003
Examples of these include: Topsin, Domark, Aproach & Endura
Several other products are mixtures

MBC: Methyl Benzimidazole Carbamates 
DMI: DeMethylation Inhibitors 
QoI: Quinone outside Inhibitors 
SDHI: Succinate dehydrogenase inhibitors 

Field applications of fungicides in the United States on soybean show control of _S. sclerotiorum_ is low to fair for QoI, DMI and MBC fungicides, and good for SDHI fungicides (The North Central Regional Committee on Soybean Diseases 2015). However, it is unknown whether efficacy is related to reduce sensitivity within populations under study. 



```{r read data and wrangling, echo = FALSE}
#
##  Reading and subsetting data,  
boscalid.data <-
  read.csv("data/boscalid_serialdilution_baseline(validationdata).csv")
  boscalid.data <- subset(boscalid.data, select = -X)
  boscalid.data$repeats <- rep_len(1:4, length.out = nrow(boscalid.data))
  boscalid.data$ID <- as.character(boscalid.data$ID)
  # renaming ID for the current names
 boscalid.data$ID[ boscalid.data$ID =="12B"]  <- "12" 
 #Although 74SS1 belong to # 74, the one what I used was specifically this:74SS1
 boscalid.data$ID[ boscalid.data$ID =="74SS1"]  <- "74" 
 boscalid.data$ID[ boscalid.data$ID =="62-02"]  <- "2098" 
 boscalid.data$ID[ boscalid.data$ID =="62-03"]  <- "2099" 
 boscalid.data$ID[ boscalid.data$ID =="62-04"]  <- "2100" 
 boscalid.data$ID[ boscalid.data$ID =="78-01"]  <- "2139" 
 boscalid.data$ID[ boscalid.data$ID =="78-02"]  <- "2140" 
 boscalid.data$ID[ boscalid.data$ID =="78-05"]  <- "2143" 
 boscalid.data$ID[ boscalid.data$ID =="S-01"]  <- "2320" 
 boscalid.data$ID[ boscalid.data$ID =="H-01"]  <- "2220" 
 boscalid.data$ID[ boscalid.data$ID =="H-03"]  <- "2222" 
 boscalid.data$ID[ boscalid.data$ID =="H-04"]  <- "2223"
 boscalid.data$ID[ boscalid.data$ID =="I-20"]  <- "2362"
 boscalid.data$ID[ boscalid.data$ID =="419"]  <- "2385"
 boscalid.data$ID[ boscalid.data$ID =="413"]  <- "2386"
 boscalid.data$ID[ boscalid.data$ID =="W212"]  <- "2388"
 boscalid.data$ID[ boscalid.data$ID =="318"]  <- "2390"

  ####Transforming to $ID to numeric
 boscalid.data$ID <- as.numeric(boscalid.data$ID)
 ## Discarding dose at 0.4 ppm and isolate 800 because it has just one experimental replication ##
 
 # Filter out 
  boscalid.data <- boscalid.data %>%
     filter(!dose ==  0.4 & !ID == 800) %>%
    mutate(polar= replace(polar, polar == 0, 0.6)) %>%  #replacing 0 cm growth for the size of plug that is 0.6
    mutate(ecuatorial= replace(ecuatorial, ecuatorial == 0, 0.6)) %>% #replacing 0 cm growth for the size of plug that is 0.6
    group_by(ID, experimental_replicate, dose, ecuatorial, polar, repeats) %>%
    mutate(growth = ((ecuatorial + polar) / 2))
    
#Reading and subsetting data picoxystrobin
  picoxystrobin.data <-
    read.csv("data/picoxystrobin_serialdi_BL-WMN_survey-WMNCSRP(validationdata).csv")
    picoxystrobin.data$repeats <- rep_len(1:4, nrow(picoxystrobin.data))
    picoxystrobin.data$ID <- as.character(picoxystrobin.data$ID)
    # renaming ID for the current names
    
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="12B"]  <- "12" 
#Although 74SS1 belong to # 74, the one what I used was specifically this:74SS
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="74SS1"]  <- "74" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="62-02"]  <- "2098" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="62-03"]  <- "2099" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="62-04"]  <- "2100" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="78-01"]  <- "2139" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="78-02"]  <- "2140" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="78-05"]  <- "2143" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="S-01"]  <- "2320" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="H-01"]  <- "2220" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="H-03"]  <- "2222" 
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="H-04"]  <- "2223"
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="I-20"]  <- "2362"
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="419"]  <- "2385"
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="413"]  <- "2386"
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="W212"]  <- "2388"
 picoxystrobin.data$ID[ picoxystrobin.data$ID =="318"]  <- "2390"

   ####Transforming to $ID to numeric
picoxystrobin.data$ID <- as.numeric(picoxystrobin.data$ID)
   
  #Filter out 
    picoxystrobin.data <- picoxystrobin.data %>%
      mutate(polar= replace(polar, polar == 0, 0.6)) %>%  #replacing 0 cm growth for the size of plug that is 0.6
    mutate(ecuatorial= replace(ecuatorial, ecuatorial == 0, 0.6)) %>% 
      group_by(ID, experimental_replicate, dose, ecuatorial, polar, repeats) %>%
      mutate(growth = ((ecuatorial + polar) / 2))
      
#Reading and subsetting data tetraconazole
tetraconazole.data <-
  read.csv("data/tetraconazole_serialdi_BL-WMN_survey-WMNCSRP(validationdata).csv")
  tetraconazole.data <- subset(tetraconazole.data, select = -(X:X.1))
  tetraconazole.data$repeats <- rep_len(1:4, length.out = nrow(tetraconazole.data))
  tetraconazole.data$ID <- as.character(tetraconazole.data$ID) 
  # renaming ID for the current names
 tetraconazole.data$ID[ tetraconazole.data$ID =="12B"]  <- "12" 
#Although 74SS1 belong to # 74, the one what I used was specifically this:74SS
 tetraconazole.data$ID[tetraconazole.data$ID == "74SS1"]  <- "74"
 tetraconazole.data$ID[tetraconazole.data$ID == "62-02"]  <- "2098"
 tetraconazole.data$ID[tetraconazole.data$ID == "62-03"]  <- "2099"
 tetraconazole.data$ID[tetraconazole.data$ID == "62-04"]  <- "2100"
 tetraconazole.data$ID[tetraconazole.data$ID == "78-01"]  <- "2139"
 tetraconazole.data$ID[tetraconazole.data$ID == "78-02"]  <- "2140"
 tetraconazole.data$ID[tetraconazole.data$ID == "78-05"]  <- "2143"
 tetraconazole.data$ID[tetraconazole.data$ID == "S-01"]  <- "2320"
 tetraconazole.data$ID[tetraconazole.data$ID == "H-01"]  <- "2220"
 tetraconazole.data$ID[tetraconazole.data$ID == "H-03"]  <- "2222"
 tetraconazole.data$ID[tetraconazole.data$ID == "H-04"]  <- "2223"
 tetraconazole.data$ID[tetraconazole.data$ID == "I-20"]  <- "2362"
 tetraconazole.data$ID[tetraconazole.data$ID == "419"]  <- "2385"
 tetraconazole.data$ID[tetraconazole.data$ID == "413"]  <- "2386"
 tetraconazole.data$ID[tetraconazole.data$ID == "W212"]  <- "2388"
 tetraconazole.data$ID[tetraconazole.data$ID == "318"]  <- "2390"
 
    ####Transforming to $ID to numeric
tetraconazole.data$ID <- as.numeric(tetraconazole.data$ID)
   # Filter out 
  tetraconazole.data <- tetraconazole.data %>%
     mutate(polar= replace(polar, polar == 0, 0.6)) %>%  #replacing 0 cm growth for the size of plug that is 0.6
    mutate(ecuatorial= replace(ecuatorial, ecuatorial == 0, 0.6)) %>% 
    group_by(ID, experimental_replicate, dose, ecuatorial, polar, repeats) %>%
    mutate(growth = ((ecuatorial + polar) / 2))
#Reading and subsetting data TM
  TMdata <-
    read.csv("data/TM_serialdi_BL-WMN_survey-WMNCSRP(validationdata).csv")
    TMdata <- subset(TMdata, select = -(X:X.6))
    TMdata$repeats <- rep_len(1:4, length.out = nrow(TMdata))
    TMdata$ID <- as.character(TMdata$ID)
   # renaming ID for the current names
  TMdata$ID[ TMdata$ID =="12B"]  <- "12" 
 #Although 74SS1 belong to # 74, the one what I used was specifically this:74SS
  TMdata$ID[TMdata$ID == "74SS1"]  <- "74"
  TMdata$ID[TMdata$ID == "62-02"]  <- "2098"
  TMdata$ID[TMdata$ID == "62-03"]  <- "2099"
  TMdata$ID[TMdata$ID == "62-04"]  <- "2100"
  TMdata$ID[TMdata$ID == "78-01"]  <- "2139"
  TMdata$ID[TMdata$ID == "78-02"]  <- "2140"
  TMdata$ID[TMdata$ID == "78-05"]  <- "2143"
  TMdata$ID[TMdata$ID == "S-01"]  <- "2320"
  TMdata$ID[TMdata$ID == "H-01"]  <- "2220"
  TMdata$ID[TMdata$ID == "H-03"]  <- "2222"
  TMdata$ID[TMdata$ID == "H-04"]  <- "2223"
  TMdata$ID[TMdata$ID == "I-20"]  <- "2362"
  TMdata$ID[TMdata$ID == "419"]  <- "2385"
  TMdata$ID[TMdata$ID == "413"]  <- "2386"
  TMdata$ID[TMdata$ID == "W212"]  <- "2388"
  TMdata$ID[TMdata$ID == "318"]  <- "2390"
  
 ####Transforming to $ID to numeric
TMdata$ID <- as.numeric(TMdata$ID)   
  #Filter out the control observations tomething weird happened with the repeats 3 so Iam revoming those
    TMdata <- TMdata %>%
      group_by(ID, experimental_replicate, dose, ecuatorial, polar, repeats) %>%
      filter(!experimental_replicate == 1 |
      !dose == 1.5 | !repeats == 3) %>% # something weird happened with the repeats 3 so Iam revoming those
      mutate(growth = ((ecuatorial + polar) / 2))
      
#Reading and subsetting data of discriminatory dose use
    survey.data <-  read.csv("data/DD_survey-WMNCSRP.csv")
    survey.data <- survey.data %>%
    group_by(
    ID,
    repeats,
    experimental_replicate,
    sham.ecuatorial,
    sham.polar,
    picoxystrobin.ecuatorial,
    picoxystrobin.polar,
    boscalid.ecuatorial,
    boscalid.polar,
    tetraconazole.ecuatorial,
    tetraconazole.polar,
    TM.ecuatorial,
    TM.polar,
    control.ecuatorial,
    control.polar
    ) %>%
        mutate(
    sham.growth = ((sham.ecuatorial + sham.polar) / 2),
    picoxystrobin.growth = ((
    picoxystrobin.ecuatorial + picoxystrobin.polar
    ) / 2),
    boscalid.growth = ((boscalid.ecuatorial + boscalid.polar) / 2),
    tetraconazole.growth = ((
    tetraconazole.ecuatorial + tetraconazole.polar
    ) / 2),
    TM.growth = ((TM.ecuatorial + TM.polar) / 2),
    control.growth = ((control.ecuatorial + control.polar) / 2)
    ) %>%
    ungroup()
    
    survey.data.2 <- survey.data
    survey.data.2$ID <- as.character(survey.data.2$ID)
     # renaming ID for the current names
    survey.data.2$ID[survey.data.2$ID == "54C"]  <- "2453"
    survey.data.2$ID[survey.data.2$ID == "65B"]  <- "2528"
    survey.data.2$ID[survey.data.2$ID == "51C"]  <- "2449"
    survey.data.2$ID[survey.data.2$ID == "71B"]  <- "2505"
    survey.data.2$ID[survey.data.2$ID == "64D"]  <- "2518"
    survey.data.2$ID[survey.data.2$ID == "53B"]  <- "2536"
    survey.data.2$ID[survey.data.2$ID == "60A"]  <- "2559"
    survey.data.2$ID[survey.data.2$ID == "H-01"]  <- "2220"
    survey.data.2$ID[survey.data.2$ID == "H-03"]  <- "2222"
    survey.data.2$ID[survey.data.2$ID == "419"]  <- "2385"
    survey.data.2$ID[survey.data.2$ID == "78-02"]  <- "2140"
    
    survey.data.3 <- survey.data.2 %>% mutate(ID = as.numeric(ID)) %>% mutate(new= "No")

  #Discriminatory dose boscalid
   
    survey.data.boscalid <-
      read.csv("data/DD_survey-WMNCSRP_boscalid.csv")
      survey.data.boscalid <- survey.data.boscalid %>%
      select(
      ID,
      repeats,
      experimental_replicate,
      control.ecuatorial_30hr,
      control.polar_30hr,
      boscalid.ecuatorial.30hr,
      boscalid.polar_30hr
      ) %>%
      mutate(
      control.growth = ((
      control.polar_30hr + control.ecuatorial_30hr
      ) / 2),
      boscalid.growth = ((
      boscalid.ecuatorial.30hr + boscalid.polar_30hr
      ) / 2),
      ID = as.character(ID),
      new = "Yes"
      ) %>%
      select(ID,
      repeats,
      experimental_replicate,
      control.growth,
      boscalid.growth,
      new)
  
     #Discriminatory dose picoxystrobin
   
      survey.data.picoxystrobin <-
        read.csv("data/DD_survey-WMNCSRP_picoxystrobin.csv")
        survey.data.picoxystrobin <- survey.data.picoxystrobin %>%
        select(
        ID,
        repeats,
        experimental_replicate,
        sham.ecuatorial,
        sham.polar,
        picoxystrobin.ecuatorial,
        picoxystrobin.polar
        ) %>%
        mutate(
        sham.growth = ((sham.ecuatorial + sham.polar) / 2),
        picoxystrobin.growth = ((
        picoxystrobin.ecuatorial + picoxystrobin.polar
        ) / 2),
        ID = as.character(ID),
        new = "Yes"
        ) %>%
        select(ID,
        repeats,
        experimental_replicate,
        sham.growth,
        picoxystrobin.growth,
        new)
        
     #Discriminatory dose tetraconazole
   
        survey.data.tetraconazole <-
          read.csv("data/DD_survey-WMNCSRP_tetraconazole.csv")
          survey.data.tetraconazole <- survey.data.tetraconazole %>%
          select(
          ID,
          repeats,
          experimental_replicate,
          control.ecuatorial,
          control.polar,
          tetraconazole.ecuatorial,
          tetraconazole.polar
          ) %>%
          mutate(
          control.growth = ((control.ecuatorial + control.polar) / 2),
          tetraconazole.growth = ((
          tetraconazole.ecuatorial + tetraconazole.polar
          ) / 2),
          ID = as.character(ID),
          new = "Yes"
          ) %>%
          select(ID,
          repeats,
          experimental_replicate,
          control.growth,
          tetraconazole.growth,
          new)
          
#Discriminatory dose TM
             
          survey.data.TM <-
            read.csv("data/DD_survey-WMNCSRP_TM.csv")
            survey.data.TM <- survey.data.TM %>%
            select(
            ID,
            repeats,
            experimental_replicate,
            control.ecuatorial,
            control.polar,
            TM.ecuatorial,
            TM.polar
            ) %>%
            mutate(
            control.growth = ((control.ecuatorial + control.polar) / 2),
            TM.growth = ((TM.ecuatorial + TM.polar) / 2),
            ID = as.character(ID),
            new = "Yes"
            ) %>%
            select(ID,
            repeats,
            experimental_replicate,
            control.growth,
            TM.growth,
            new)
        

# reading the inventory Sclerotinia collection with some of my update modifications
                            WM <- read.csv("data/WM-fixingproductnamesID2573_modifyingforactiveingredient_10.csv", stringsAsFactors = TRUE)
WM$Collection_ID <- str_squish(WM$Collection_ID)
# removing those isolates that are repated and have subsequent ID number becasue they are coming from the previous isolates, for example, 5 & 5A,both are the same, actually 5A is coming from 5,  removing then 5A
WM2 <- 
WM %>% filter(
  !Collection_ID == "5A",
  !Collection_ID == "12Ba",
  !Collection_ID == "12Bb",
  !Collection_ID == "13Bb",
  !Collection_ID == "13Ba",
  !Collection_ID == "13Bb",
  !Collection_ID == "13Bc",
  !Collection_ID == "13E",
  !Collection_ID == "13Ea",
  !Collection_ID == "13Eb",
  !Collection_ID == "13Ec",
  !Collection_ID == "15a",
  !Collection_ID == "15b",
  !Collection_ID == "15c",
  !Collection_ID == "19a",
  !Collection_ID == "19b",
  !Collection_ID == "19c",
  !Collection_ID == "74",
  !Collection_ID == "74-SS-2",
  # removed this one becuase the one used was 74-SS1
  !Collection_ID == "74a",
  !Collection_ID == "74b",
  !Collection_ID == "74c",
  !Collection_ID == "136a",
  !Collection_ID == "136b",
  !Collection_ID == "136c",
  !Collection_ID == "143a",
  !Collection_ID == "143b",
  !Collection_ID == "143c",
  !Collection_ID == "143d",
  !Collection_ID == "143e",
  !Collection_ID == "143f",
  !Collection_ID == "147b",
  !Collection_ID == "147c",
  !Collection_ID == "152a",
  !Collection_ID == "152b",
  !Collection_ID == "152c",
  !Collection_ID == "152d",
  !Collection_ID == "152e",
  !Collection_ID == "152f",
  !Collection_ID == "152g",
  !Collection_ID == "152h",
  !Collection_ID == "152i",
  !Collection_ID == "152j",
  !Collection_ID == "152JR",
  !Collection_ID == "160a",
  !Collection_ID == "160b",
  !Collection_ID == "160c",
  !Collection_ID == "161a",
  !Collection_ID == "161b",
  !Collection_ID == "161c",
  !Collection_ID == "167a",
  !Collection_ID == "167b",
  !Collection_ID == "167c",
  !Collection_ID == "184a",
  !Collection_ID == "184b",
  !Collection_ID == "184c",
  !Collection_ID == "202a",
  !Collection_ID == "202b",
  !Collection_ID == "202c",
  !Collection_ID == "232B",
  !Collection_ID == "245a",
  !Collection_ID == "245b",
  !Collection_ID == "245c",
  !Collection_ID == "247a",
  !Collection_ID == "247b",
  !Collection_ID == "247c",
  !Collection_ID == "248a",
  !Collection_ID == "248b",
  !Collection_ID == "262a",## Any belonging to 262  because it is S trifoliorum
  !Collection_ID == "262b",
  !Collection_ID == "264a",
  !Collection_ID == "264b",
  !Collection_ID == "136c",
  !Collection_ID == "264c",
  !Collection_ID == "274a",
  !Collection_ID == "274b",
  !Collection_ID == "334a",
  !Collection_ID == "334b",
  !Collection_ID == "334c",
  !Collection_ID == "336a",
  !Collection_ID == "336b",
  !Collection_ID == "336c",
  !Collection_ID == "339a",
  !Collection_ID == "339b",
  !Collection_ID == "339c",
  !Collection_ID == "339d",
  !Collection_ID == "339e",
  !Collection_ID == "339f",
  !Collection_ID == "341a",
  !Collection_ID == "341b",
  !Collection_ID == "341c",
  !Collection_ID == "324a",
  !Collection_ID == "342a",
  !Collection_ID == "342b",
  !Collection_ID == "342c",
  !Collection_ID == "346a",
  !Collection_ID == "346b",
  !Collection_ID == "346c",
  !Collection_ID == "353b",
  !Collection_ID == "354a",
  !Collection_ID == "354b",
  !Collection_ID == "354c",
  !Collection_ID == "360b",
  !Collection_ID == "360c",
  !Collection_ID == "361b",
  !Collection_ID == "361c",
  !Collection_ID == "362b",
  !Collection_ID == "362c",
  !Collection_ID == "363b",
  !Collection_ID == "363c",
  !Collection_ID == "364b",
  !Collection_ID == "364c",
  !Collection_ID == "365b",
  !Collection_ID == "365c",
  !Collection_ID == "366b",
  !Collection_ID == "366c",
  !Collection_ID == "367b",
  !Collection_ID == "367c",
  !Collection_ID == "368b",
  !Collection_ID == "368c",
  !Collection_ID == "369b",
  !Collection_ID == "369c",
  !Collection_ID == "370b",
  !Collection_ID == "370c",
  !Collection_ID == "371b",
  !Collection_ID == "371c",
  !Collection_ID == "372b",
  !Collection_ID == "372c",
  !Collection_ID == "373b",
  !Collection_ID == "373c",
  !Collection_ID == "374b",
  !Collection_ID == "374c",
  !Collection_ID == "375a",
  !Collection_ID == "375b",
  !Collection_ID == "376b",
  !Collection_ID == "376c",
  !Collection_ID == "377b",
  !Collection_ID == "377c",
  !Collection_ID == "400a",
  !Collection_ID == "400b",
  !Collection_ID == "973A",
  !Collection_ID == "973B",
  !Collection_ID == "973C",
  !Collection_ID == "973D",
  !Collection_ID == "973E",
  !Collection_ID == "974A",
  !Collection_ID == "974B",
  !Collection_ID == "974C",
  !Collection_ID == "974D",
  !Collection_ID == "974E",
  !Collection_ID == "975A",
  !Collection_ID == "975B",
  !Collection_ID == "975C",
  !Collection_ID == "975D",
  !Collection_ID == "975E",
  !Collection_ID == "976A",
  !Collection_ID == "976B",
  !Collection_ID == "976C",
  !Collection_ID == "976D",
  !Collection_ID == "976E",
  !Collection_ID == "977A",
  !Collection_ID == "977B",
  !Collection_ID == "977C",
  !Collection_ID == "977D",
  !Collection_ID == "977E",
  !Collection_ID == "978A",
  !Collection_ID == "978B",
  !Collection_ID == "978C",
  !Collection_ID == "978D",
  !Collection_ID == "978E",
  !Collection_ID == "979A",
  !Collection_ID == "979B",
  !Collection_ID == "979C",
  !Collection_ID == "979D",
  !Collection_ID == "979E",
  # These are cross out on the inventory list
  !Collection_ID == "1048",
  !Collection_ID == "1049",
  !Collection_ID == "1227",
  !Collection_ID == "1228",
  !Collection_ID == "2217",
  !Collection_ID == "2219",
  !Collection_ID == "2225",
  !Collection_ID == "2226",
  !Collection_ID == "2230",
  !Collection_ID == "2245",
  !Collection_ID == "2307",
  !Collection_ID == "2320",
  !Collection_ID == "2325",
  !Collection_ID == "2327",
  !Collection_ID == "2329",
  !Collection_ID == "2352",
  !Collection_ID == "2366",
  !Collection_ID == "2367",
  !Collection_ID == "2369",
  !Collection_ID == "2373",
  !Collection_ID == "2375",
  !Collection_ID == "2380",
  !Collection_ID == "2387",
  !Collection_ID == "2389",
  !Collection_ID == "2392",
  !Collection_ID == "973D",
  # cleaning thsi isolates that are useless becuase non information
  !Collection_ID == "429",
  !Collection_ID == "433",
  !Collection_ID == "442",
  !Collection_ID == "1048",
  !Collection_ID == "1049",
  !Collection_ID == "2217",
  !Collection_ID == "2219",
  !Collection_ID == "2226",
  !Collection_ID == "2245",
  !Collection_ID == "2307",
  !Collection_ID == "2327",
  !Collection_ID == "2352",
  !Collection_ID == "2366",
  !Collection_ID == "2367",
  !Collection_ID == "2380",
  !Collection_ID == "2392", 
  !Collection_ID == "2343",  #Yuba Experiment not enough information
!Collection_ID== "2344", #Yuba Experiment
!Collection_ID== "2345", #Yuba Experiment
!Collection_ID== "2346", #Yuba Experiment
!Collection_ID== "2347", #Yuba Experiment
!Collection_ID== "2348", #Yuba Experiment
!Collection_ID== "2349", #Yuba Experiment
!Collection_ID== "2350", #Yuba Experiment
!Collection_ID== "2351", #Yuba Experiment
!Collection_ID== "2352", #Yuba Experiment
!Collection_ID== "2353", #Yuba Experiment
!Collection_ID== "2354", #Yuba Experiment
!Collection_ID== "2355", #Yuba Experiment
!Collection_ID== "2356", #Yuba Experiment
!Collection_ID== "2357", #Yuba Experiment
!Collection_ID== "2358", #Yuba Experiment
!Collection_ID== "2359", #Yuba Experiment
!Collection_ID== "2360", #Yuba Experiment
!Collection_ID== "2361", #Yuba Experiment
!Collection_ID== "2362", #Yuba Experiment
!Collection_ID== "2363", #Yuba Experiment
!Collection_ID== "2364", #Yuba Experiment
!Collection_ID== "2365", #Yuba Experiment
!Collection_ID== "2366", #Yuba Experiment
!Collection_ID== "2367", #Yuba Experiment
!Collection_ID== "2368", #Yuba Experiment
!Collection_ID== "2369", #Yuba Experiment
!Collection_ID== "2370", #Yuba Experiment
!Collection_ID== "2371", #Yuba Experiment
!Collection_ID== "2372", #Yuba Experiment
!Collection_ID== "2373", #Yuba Experiment
!Collection_ID== "2374", #Yuba Experiment
!Collection_ID== "2375", #Yuba Experiment
!Collection_ID== "2376", #Yuba Experiment
!Collection_ID== "2377", #Yuba Experiment
!Collection_ID== "2378", #Yuba Experiment
!Collection_ID== "2379", #Yuba Experiment
!Collection_ID== "2380", #Yuba Experiment
!Collection_ID== "2381" #Yuba Experiment
  ) %>% 
  rename(ID= Collection_ID)
  # Since here changing the names, for example there is no 12, it goes directly to 12B, so this 12B is gonna be the 12 now
WM2$ID[ WM2$ID =="12B"]  <- "12"
WM2$ID[ WM2$ID =="13B"]  <- "13"
 #Although 74SS1 belong to # 74 the that I used was specifically this, 74SS1
WM2$ID[ WM2$ID =="74-SS-1"]  <- "74"
WM2$ID[ WM2$ID =="125 SS-4"]  <- "125"
WM2$ID[ WM2$ID =="232A"]  <- "232"
WM2$ID[ WM2$ID =="359b"]  <- "359"
WM2$ID[ WM2$ID =="360a"]  <- "360"
WM2$ID[ WM2$ID =="361a"]  <- "361"
WM2$ID[ WM2$ID =="362a"]  <- "362"
WM2$ID[ WM2$ID =="363a"]  <- "363"
WM2$ID[ WM2$ID =="364a"]  <- "364"
WM2$ID[ WM2$ID =="365a"]  <- "365"
WM2$ID[ WM2$ID =="366a"]  <- "366"
WM2$ID[ WM2$ID =="367a"]  <- "367"
WM2$ID[ WM2$ID =="368a"]  <- "368"
WM2$ID[ WM2$ID =="369a"]  <- "369"
WM2$ID[ WM2$ID =="370a"]  <- "370"
WM2$ID[ WM2$ID =="371a"]  <- "371"
WM2$ID[ WM2$ID =="372a"]  <- "372"
WM2$ID[ WM2$ID =="373a"]  <- "373"
WM2$ID[ WM2$ID =="374a"]  <- "374"
WM2$ID[ WM2$ID =="375c"]  <- "375"
WM2$ID[ WM2$ID =="376a"]  <- "376"
WM2$ID[ WM2$ID =="377a"]  <- "377"

  
 


```

```{r}
WM3 <- WM2 %>% mutate(
  ID = as.numeric(ID),
  long = as.numeric(as.character(long)), 
       long =  long * -1, 
      DNA.Extraction = recode(DNA.Extraction, 
      No = "No DNA extraction",
      Yes = "Yes DNA extraction", .default = "No DNA extraction") 
  )

```

# Hypotheses  

1. Some _S. sclerotiorum_ isolates from fungicide field trials and farmer fields will have decreased sensitivity to commonly used fungicides in the U.S.  

2. Some _S. sclerotiorum_ isolates from dry beans will have decreased sensitivity compared to those from soybeans.

```{r setting objects and wrangling, echo = FALSE}
#replacing with the sourceal ID, for example, instead of 12b, now 12

baseline_isolates <- c(1, 8, 12, 20, 21, 74, 87, 118, 123, 129, 449, 461, 467, 475, 558, 564, 568, 581, 645, 667, 800) #Some baseline isolates arbitrarily selected; included those old and from white mold nursery

survey_isolates <-  c( 2385, 2386, 2098, 2099, 2100, 2139, 2140, 2143, 2220, 2222, 2223, 2320, 2362, 2388, 2390 ) #Some farmer field isolates arbitrarily selected

Farmer_fields <- c(136:442, 455, 456, 466, 468, 470, 471, 478:554, 602:610, 612:635, 671, 672, 682:690, 695:797, 810:823, 834, 835, 848:1024, 1255: 1326, 1491: 1500, 1661:1670, 1831: 2246, 2303: 2342,2362: 2381, 2393: 2573) # All  farmer field isolates 

baseline_isolates_2 <- c(1: 136, 444: 454, 457: 465, 467, 469, 472:477, 555:601, 611, 636:670, 673: 680, 691:694 , 798: 809,  824: 833, 836: 847) # All  baselie isolates; included old isolates () and white mold nurseries

drybean <- c(1, 5, 12,13:118, 123:128, 133:135, 145, 146, 152, 155:160, 182: 185, 194:200, 205, 220, 223, 248, 253:255, 274, 279, 280, 290, 294, 304: 309, 323, 358, 393, 395, 396, 397, 400:402, 405, 408, 409, 434, 443:465, 467, 469: 493, 495:505, 555:613, 615: 760, 762: 819, 824:833, 835:855, 858:921, 966: 971, 980, 981, 985: 996, 998: 1009, 1220:1225 , 1857: 1940, 2242: 2569) # All  dry bean isolates

soybean <- c(143, 147, 181, 187, 188, 189,202, 257: 259, 264:268, 276, 281, 289, 293, 295, 310 , 399, 412:417, 419, 425:427, 439, 440, 494, 506:554, 834, 972:979, 982, 997, 1010: 1022, 1025:1219, 1229: 1856, 1941: 2241 ) # All  soybean isolates

SI_Production_Field <- c( 698:741, 743:744, 746:760, 762: 778, 
786: 797, 810:819, 848: 855, 858: 914) # All isolates under nomenclature SI_Production_Field 

SI_Screening_Nursery_Field <- c(444:454, 457:465, 467, 469, 472:477, 555: 582, 584: 601, 611, 636:670, 673:681,691:694, 798:809, 824: 833 , 836:847)# # All isolates under nomenclature SI_Screening_Nursery_Field; also included "WM Monitor"" 

potato <- c(2570:2573) # All isolates from potato

mexican.isolates <- c(242, 248, 615:632, 779, 1857: 1940) # All isolates from Mexico
brazilian.isolates <-  c(400:402, 972:979, 1010:1022, 1227:1254, 2417:2569) # All isolates from Brazil


#Fungicides single mode of action
Group_one <- c("thiophanate_methyl")
Group_3 <- c( "prothioconazole", "tetraconazole", "flutriafol", "propiconazole", "tebuconazole", "difenoconazole")
Group_7 <- c("fluxapyroxad", "boscalid")
Group_11 <- c("picoxystrobin", "azoxystrobin", "fluoxastrobin", "pyraclostrobin", "trifloxystrobin")

not_considered <- c("potassium phosphite")

#Mixes of fungicides IN COMERCIAL PRODUCTS

 Group_3_Group_11 <-  c(
   "flutriafol + fluoxastrobin",
   "tetraconazole + pyraclostrobin", #there 2 fungicides: single MOA(tetraconazole) + single MOA( pyraclostrobin) #Put attention for the mixes analyses with 2 single MOA!!
   "propiconazole + azoxystrobin",
"prothioconazole + trifloxystrobin", 
"tetraconazole + fluatriafol + fluxastrobin", #there 2 fungicides: single MOA(tetraconazole) + mix( flutriafol + fluxastrobin) #Put attention for the mixes analyses with 2 single MOA!!
"difenoconazole + azoxystrobin")
 
Group_7_Group_11 <- c(
  "fluxapyroxad + pyraclostrobin", 
  "pyraclostrobin + fluxapyroxad + pyraclostrobin")  #there 2 fungicides: single MOA (pyraclostrobin) + mix (fluxapyroxad + pyraclostrobin) #Put attention for the mixesanalyses with 2 single MOA!!                     
                     
 Group_3_not_considered <- "tebuconazole + potassium phosphite"
 
  unknown <- c("No_info")
 
#converting these levels of factors where is NA in now unknown
  
  

levels(WM3$Fungicide_current_season)[levels(WM3$Fungicide_current_season) == ""] <- "unknown"

levels(WM3$molecule.s._current_season)[levels(WM3$molecule.s._current_season) == ""] <- "unknown"

levels(WM3$molecule.s._current_season)[levels(WM3$molecule.s._current_season) == "No_info"] <- "unknown"

levels(WM3$Fungicide_previous_seasons)[levels(WM3$Fungicide_previous_seasons) == ""] <- "unknown"


levels(WM3$molecule.s._previous_seasons)[levels(WM3$molecule.s._previous_seasons) == ""] <- "unknown"



WM3_ <- WM3%>%
  # transforming this variable in character
  mutate(molecule.s._current_season = as.character(WM3$molecule.s._current_season)) %>% 
  #creating a new variable called Group_MOA based if they are in the corresponding objects, if not is named "unknown" 
  mutate(
    Group_MOA_current_season = case_when(
       molecule.s._current_season%in% Group_one ~ "Group_one",# filtering and naming "the name of the group" in case of in
       molecule.s._current_season%in% Group_3~ "Group_3",
       molecule.s._current_season%in% Group_7 ~ "Group_7",
       molecule.s._current_season%in% Group_11 ~ "Group_11", molecule.s._current_season%in% Group_3_Group_11~ "Group_3&Group_11",
       molecule.s._current_season%in% Group_7_Group_11~ "Group_7&Group_11",
       molecule.s._current_season%in% Group_3_not_considered~ "Group_3&not_considered",
       molecule.s._current_season%in% unknown~ "unknown", #this consider the control CHECK this out unknown
             TRUE ~ "unknown"# in case of not, naming "not_selected""
    ), 
    Group_MOA_previous_seasons = case_when(
       molecule.s._previous_seasons%in% Group_one ~ "Group_one",# filtering and naming "the name of the group" in case of in
       molecule.s._previous_seasons%in% Group_3~ "Group_3",
       molecule.s._previous_seasons%in% Group_7 ~ "Group_7",
       molecule.s._previous_seasons%in% Group_11 ~ "Group_11", molecule.s._previous_seasons%in% Group_3_Group_11~ "Group_3&Group_11",
       molecule.s._previous_seasons%in% Group_7_Group_11~ "Group_7&Group_11",
       molecule.s._previous_seasons%in% Group_3_not_considered~ "Group_3&not_considered",
       molecule.s._previous_seasons%in% unknown~ "unknown", #this consider the control CHECK this out unknown
             TRUE ~ "unknown"# in case of not, naming "not_selected""
    ) )  %>%  
mutate(Field_Names= paste( Year,Field, sep = "_")) 

 # Summarizing for table for publication
  WM_publication <- WM3_ %>% 
    filter(Year == 2015 | Year == 2016 | Year == 2017) %>%
  ungroup() %>%
  group_by(State, Field, Year, molecule.s._current_season, Rate ) %>%
  summarize(N_isolates= n()) %>%
    ungroup() %>%
    add_row(State = "Total", N_isolates = sum(.$N_isolates))
 
# Creating a pdf  
 WM_publication %>% kable(format = "markdown",caption = "Table with outliers for each fungicide, NA= never tested, 0= not an outlier but tested, 1= outlier", padding = 0, align = "l") %>%
  write2pdf("table_publication.pdf")

 # Creating object from the last object by State
WM_AB  <- WM3_ %>%
  filter(WM3_$State== "AB") %>% 
  pull(ID)
 WM_AZ  <- WM3_ %>%
  filter(WM3_$State== "AZ") %>% 
  pull(ID)
WM_BA  <- WM3_ %>%
  filter(WM3_$State== "BA") %>% 
  pull(ID)
 WM_CA  <- WM3_ %>%
  filter(WM3_$State== "CA") %>% 
  pull(ID)
 
WM_CO  <- WM3_ %>%
  filter(WM3_$State== "CO") %>% 
  pull(ID)
 WM_DE  <- WM3_ %>%
  filter(WM3_$State== "DE") %>% 
  pull(ID)
 WM_DF  <- WM3_ %>%
  filter(WM3_$State== "DF") %>% 
  pull(ID)
 WM_FL  <- WM3_ %>%
  filter(WM3_$State== "FL") %>% 
  pull(ID)
 WM_GA  <- WM3_ %>%
  filter(WM3_$State== "GA") %>% 
  pull(ID)
 WM_GO  <- WM3_ %>%
  filter(WM3_$State== "GO") %>% 
  pull(ID)
 WM_IA  <- WM3_ %>%
  filter(WM3_$State== "IA") %>% 
  pull(ID)
 WM_ID  <- WM3_ %>%
  filter(WM3_$State== "ID") %>% 
  pull(ID)
 WM_KS  <- WM3_ %>%
  filter(WM3_$State== "KS") %>% 
  pull(ID)
 WM_KY  <- WM3_ %>%
  filter(WM3_$State== "KY") %>% 
  pull(ID)
 WM_LA  <- WM3_ %>%
  filter(WM3_$State== "LA") %>% 
  pull(ID)
 WM_MD  <- WM3_ %>%
  filter(WM3_$State== "MD") %>% 
  pull(ID)
 WM_MG  <- WM3_ %>%
  filter(WM3_$State== "MG") %>% 
  pull(ID)
 WM_MI  <- WM3_ %>%
  filter(WM3_$State== "MI") %>% 
  pull(ID)
 WM_MN  <- WM3_ %>%
  filter(WM3_$State== "MN") %>% 
  pull(ID)
 WM_MO  <- WM3_ %>%
  filter(WM3_$State== "MO") %>% 
  pull(ID)
 WM_MS  <- WM3_ %>%
  filter(WM3_$State== "MS") %>% 
  pull(ID)
 WM_MT  <- WM3_ %>%
  filter(WM3_$State== "MT") %>% 
  pull(ID)
 WM_NC  <- WM3_ %>%
  filter(WM3_$State== "NC") %>% 
  pull(ID)
 WM_ND  <- WM3_ %>%
  filter(WM3_$State== "ND") %>% 
  pull(ID)
 WM_NE  <- WM3_ %>%
  filter(WM3_$State== "NE") %>% 
  pull(ID)
 WM_NY  <- WM3_ %>%
  filter(WM3_$State== "NY") %>% 
  pull(ID)
 WM_OH  <- WM3_ %>%
  filter(WM3_$State== "OH") %>% 
  pull(ID)
 WM_OK  <- WM3_ %>%
  filter(WM3_$State== "OK") %>% 
  pull(ID)
 WM_ON  <- WM3_ %>%
  filter(WM3_$State== "ON") %>% 
  pull(ID)
 WM_OR  <- WM3_ %>%
  filter(WM3_$State== "OR") %>% 
  pull(ID)
 WM_PA  <- WM3_ %>%
  filter(WM3_$State== "PA") %>% 
  pull(ID)
 WM_PR  <- WM3_ %>%
  filter(WM3_$State== "PR") %>% 
  pull(ID)
 WM_QUE  <- WM3_ %>%
  filter(WM3_$State== "QUE") %>% 
  pull(ID)
 WM_RS  <- WM3_ %>%
  filter(WM3_$State== "RS") %>% 
  pull(ID)
 WM_SC  <- WM3_ %>%
  filter(WM3_$State== "SC") %>% 
  pull(ID)
 WM_SIN  <- WM3_ %>%
  filter(WM3_$State== "SIN") %>% 
  pull(ID)
 WM_SK  <- WM3_ %>%
  filter(WM3_$State== "SK") %>% 
  pull(ID)
 WM_WI  <- WM3_ %>%
  filter(WM3_$State== "WI") %>% 
  pull(ID)
 WM_WA  <- WM3_ %>%
  filter(WM3_$State== "WA") %>% 
  pull(ID)
 
 # Creating object from the last object by Field_Names
WM_1963  <- WM3_ %>%
  filter(WM3_$Field_Names== "1963_") %>% 
  pull(ID)

 WM_1965<- WM3_ %>%
  filter(WM3_$Field_Names== "1965_") %>% 
  pull(ID)

 WM_1969<- WM3_ %>%
  filter(WM3_$Field_Names== "1969_") %>% 
  pull(ID)

 WM_1973<- WM3_ %>%
  filter(WM3_$Field_Names== "1973_") %>% 
  pull(ID)

 WM_1974<- WM3_ %>%
  filter(WM3_$Field_Names== "1974_") %>% 
  pull(ID)

WM_1975 <- WM3_ %>%
  filter(WM3_$Field_Names== "1975_") %>% 
  pull(ID)

 WM_1976<- WM3_ %>%
  filter(WM3_$Field_Names== "1976_") %>% 
  pull(ID)

WM_1977 <- WM3_ %>%
  filter(WM3_$Field_Names== "1977_") %>% 
  pull(ID)

 WM_1978<- WM3_ %>%
  filter(WM3_$Field_Names== "1978_") %>% 
  pull(ID)

WM_1979 <- WM3_ %>%
  filter(WM3_$Field_Names== "1979_") %>% 
  pull(ID)

 WM_1980<- WM3_ %>%
  filter(WM3_$Field_Names== "1980_") %>% 
  pull(ID)

 WM_1981<- WM3_ %>%
  filter(WM3_$Field_Names== "1981_") %>% 
  pull(ID)

 WM_1982<- WM3_ %>%
  filter(WM3_$Field_Names== "1982_") %>% 
  pull(ID)

WM_1983 <- WM3_ %>%
  filter(WM3_$Field_Names== "1983_") %>% 
  pull(ID)

 WM_1984<- WM3_ %>%
  filter(WM3_$Field_Names== "1984_") %>% 
  pull(ID)

 WM_1985<- WM3_ %>%
  filter(WM3_$Field_Names== "1985") %>% 
  pull(ID)

 WM_1987<- WM3_ %>%
  filter(WM3_$Field_Names== "1987_") %>% 
  pull(ID)

 WM_1989<- WM3_ %>%
  filter(WM3_$Field_Names== "1989_") %>% 
  pull(ID)

 WM_1990<- WM3_ %>%
  filter(WM3_$Field_Names== "1990_") %>% 
  pull(ID)

WM_1991 <- WM3_ %>%
  filter(WM3_$Field_Names== "1991_") %>% 
  pull(ID)

 WM_1992<- WM3_ %>%
  filter(WM3_$Field_Names== "1992_") %>% 
  pull(ID)

 WM_1993<- WM3_ %>%
  filter(WM3_$Field_Names== "1993_") %>% 
  pull(ID)

 WM_1994<- WM3_ %>%
  filter(WM3_$Field_Names== "1994_") %>% 
  pull(ID)

 WM_1995<- WM3_ %>%
  filter(WM3_$Field_Names== "1995_") %>% 
  pull(ID)

 WM_1996<- WM3_ %>%
  filter(WM3_$Field_Names== "1996_") %>% 
  pull(ID)

 WM_1997<- WM3_ %>%
  filter(WM3_$Field_Names== "1997_") %>% 
  pull(ID)

 WM_1997_WM_production_31<- WM3_ %>%
  filter(WM3_$Field_Names== "1997_WM_production_31") %>% 
  pull(ID)

 WM_1997_WM_production_32<- WM3_ %>%
  filter(WM3_$Field_Names== "1997_WM_production_32") %>% 
  pull(ID)

 WM_1988<- WM3_ %>%
  filter(WM3_$Field_Names== "1988_") %>% 
  pull(ID)

 WM_1998<- WM3_ %>%
  filter(WM3_$Field_Names== "1998_") %>% 
  pull(ID)

 WM_1999<- WM3_ %>%
  filter(WM3_$Field_Names== "1999_") %>% 
  pull(ID)

 WM_2000<- WM3_ %>%
  filter(WM3_$Field_Names== "2000_") %>% 
  pull(ID)

 WM_2002<- WM3_ %>%
  filter(WM3_$Field_Names== "2002_") %>% 
  pull(ID)

 WM_2003<- WM3_ %>%
  filter(WM3_$Field_Names== "2003_") %>% 
  pull(ID)

 WM_1997_WM_production_33<- WM3_ %>%
  filter(WM3_$Field_Names== "1997_WM_production_33") %>% 
  pull(ID)

 WM_2003_WM_nursery_1<- WM3_ %>%
  filter(WM3_$Field_Names== "2003_WM_nursery_1") %>% 
  pull(ID)

 WM_2003_WM_nursery_2<- WM3_ %>%
  filter(WM3_$Field_Names== "2003_WM_nursery_2") %>% 
  pull(ID)

 WM_2003_WM_nursery_3<- WM3_ %>%
  filter(WM3_$Field_Names== "2003_WM_nursery_3") %>% 
  pull(ID)

 WM_1996_WM_nursery_4<- WM3_ %>%
  filter(WM3_$Field_Names== "1996_WM_nursery_4") %>% 
  pull(ID)

 WM_2003_WM_nursery_5<- WM3_ %>%
  filter(WM3_$Field_Names== "2003_WM_nursery_5") %>% 
  pull(ID)

 WM_2004<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_") %>% 
  pull(ID)

 WM_2005<- WM3_ %>%
  filter(WM3_$Field_Names== "2005_") %>% 
  pull(ID)

 WM_2006<- WM3_ %>%
  filter(WM3_$Field_Names== "2006_") %>% 
  pull(ID)

 WM_2004_WM_nursery_6<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_WM_nursery_6") %>% 
  pull(ID)

 WM_2004_WM_nursery_7<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_WM_nursery_7") %>% 
  pull(ID)

 WM_2004_WM_nursery_8<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_WM_nursery_8") %>% 
  pull(ID)

 WM_2004_WM_nursery_9<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_WM_nursery_9") %>% 
  pull(ID)

 WM_2004_WM_nursery_10<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_WM_nursery_10") %>% 
  pull(ID)

 WM_2004_WM_nursery_11<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_WM_nursery_11") %>% 
  pull(ID)

 WM_2004_WM_nursery_12<- WM3_ %>%
  filter(WM3_$Field_Names== "2004_WM_nursery_12") %>% 
  pull(ID)

 WM_2005_WM_nursery_13<- WM3_ %>%
  filter(WM3_$Field_Names== "2005_WM_nursery_13") %>% 
  pull(ID)

 WM_2005_WM_nursery_14<- WM3_ %>%
  filter(WM3_$Field_Names== "2005_WM_nursery_14") %>% 
  pull(ID)

 WM_2005_WM_nursery_15<- WM3_ %>%
  filter(WM3_$Field_Names== "2005_WM_nursery_15") %>% 
  pull(ID)

 WM_2005_WM_nursery_16<- WM3_ %>%
  filter(WM3_$Field_Names== "2005_WM_nursery_16") %>% 
  pull(ID)

 WM_2005_WM_nursery_17<- WM3_ %>%
  filter(WM3_$Field_Names== "2005_WM_nursery_17") %>% 
  pull(ID)

 WM_2005_WM_nursery_18<- WM3_ %>%
  filter(WM3_$Field_Names== "2005_WM_nursery_18") %>% 
  pull(ID)

 WM_2006_WM_nursery_19<- WM3_ %>%
  filter(WM3_$Field_Names== "2006_WM_nursery_19") %>% 
  pull(ID)

 WM_2007<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_") %>% 
  pull(ID)

 WM_2007_WM_production_1<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_1") %>% 
  pull(ID)

 WM_2007_WM_production_2<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_2") %>% 
  pull(ID)

 WM_2007_WM_production_3<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_3") %>% 
  pull(ID)

 WM_2007_WM_production_4<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_4") %>% 
  pull(ID)

 WM_2007_WM_production_5<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_5") %>% 
  pull(ID)

 WM_2007_WM_production_6<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_6") %>% 
  pull(ID)

 WM_2007_WM_production_7<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_7") %>% 
  pull(ID)

 WM_2007_WM_production_8<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_8") %>% 
  pull(ID)

 WM_2007_WM_production_9<- WM3_ %>%
  filter(WM3_$Field_Names== "2007_WM_production_9") %>% 
  pull(ID)

 WM_2008<- WM3_ %>%
  filter(WM3_$Field_Names== "2008_") %>% 
  pull(ID)

 WM_2008_WM_production_10<- WM3_ %>%
  filter(WM3_$Field_Names== "2008_WM_production_10") %>% 
  pull(ID)

 WM_2008_WM_nursery_20<- WM3_ %>%
  filter(WM3_$Field_Names== "2008_WM_nursery_20") %>% 
  pull(ID)

 WM_2008_WM_production_11<- WM3_ %>%
  filter(WM3_$Field_Names== "2008_WM_production_11") %>% 
  pull(ID)

 WM_2008_WM_production_12<- WM3_ %>%
  filter(WM3_$Field_Names== "2008_WM_production_12") %>% 
  pull(ID)

 WM_2008_WM_production_13<- WM3_ %>%
  filter(WM3_$Field_Names== "2008_WM_production_13") %>% 
  pull(ID)

 WM_2009<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_") %>% 
  pull(ID)

 WM_2008_WM_nursery_21<- WM3_ %>%
  filter(WM3_$Field_Names== "2008_WM_nursery_21") %>% 
  pull(ID)

 WM_2009_WM_nursery_22<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_nursery_22") %>% 
  pull(ID)

 WM_2009_WM_nursery_23<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_nursery_23") %>% 
  pull(ID)

 WM_2009_WM_production_14<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_production_14") %>% 
  pull(ID)

 WM_2009_WM_production_15<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_production_15") %>% 
  pull(ID)

 WM_2009_WM_production_16<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_production_16") %>% 
  pull(ID)

 WM_2009_WM_production_17<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_production_17") %>% 
  pull(ID)

 WM_2009_WM_production_18<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_production_18") %>% 
  pull(ID)

 WM_2009_WM_production_19<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_production_19") %>% 
  pull(ID)

 WM_2009_WM_production_20<- WM3_ %>%
  filter(WM3_$Field_Names== "2009_WM_production_20") %>% 
  pull(ID)

 WM_2010_WM_production_21<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_21") %>% 
  pull(ID)

 WM_2010_WM_production_22<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_22") %>% 
  pull(ID)

 WM_2010_WM_production_23<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_23") %>% 
  pull(ID)

 WM_2010_WM_production_24<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_24") %>% 
  pull(ID)

 WM_2010_WM_production_25<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_25") %>% 
  pull(ID)

 WM_2010_WM_production_26<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_26") %>% 
  pull(ID)

 WM_2010_WM_production_27<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_27") %>% 
  pull(ID)

 WM_2010_WM_production_28<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_28") %>% 
  pull(ID)

 WM_2010_WM_production_29<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_29") %>% 
  pull(ID)

 WM_2010_WM_production_30<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_WM_production_30") %>% 
  pull(ID)

 WM_2011<- WM3_ %>%
  filter(WM3_$Field_Names== "2011_") %>% 
  pull(ID)

 WM_2012<- WM3_ %>%
  filter(WM3_$Field_Names== "2012_") %>% 
  pull(ID)

 WM_2013<- WM3_ %>%
  filter(WM3_$Field_Names== "2013_") %>% 
  pull(ID)

 WM_2014<- WM3_ %>%
  filter(WM3_$Field_Names== "2014_") %>% 
  pull(ID)

 WM_2016<- WM3_ %>%
  filter(WM3_$Field_Names== "2016_") %>% 
  pull(ID)

 WM_2016_po<- WM3_ %>%
  filter(WM3_$Field_Names== "2016_po") %>% 
  pull(ID)

 WM_2016_flo<- WM3_ %>%
  filter(WM3_$Field_Names== "2016_flo") %>% 
  pull(ID)

 WM_2016_lan<- WM3_ %>%
  filter(WM3_$Field_Names== "2016_lan") %>% 
  pull(ID)

 WM_2017_ho<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_ho") %>% 
  pull(ID)

 WM_2017_an<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_an") %>% 
  pull(ID)

 WM_2017_dod<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_dod") %>% 
  pull(ID)

 WM_2017_va<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_va") %>% 
  pull(ID)

 WM_2017_na<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_na") %>% 
  pull(ID)

 WM_2017_sa<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_sa") %>% 
  pull(ID)

 WM_2017_ha<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_han") %>% 
  pull(ID)

 WM_2017_cu<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_cu") %>% 
  pull(ID)

 WM_2017_mon<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_mon") %>% 
  pull(ID)

 WM_2017_ant<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_ant") %>% 
  pull(ID)

 WM_2017_holt<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_holt") %>% 
  pull(ID)

 WM_2017_arr<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_arr") %>% 
  pull(ID)

 WM_2017_ini<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_ini") %>% 
  pull(ID)

 WM_2017_ley<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_ley") %>% 
  pull(ID)

 WM_2017_pre<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_pre") %>% 
  pull(ID)

 WM_2017_ru<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_ru") %>% 
  pull(ID)

 WM_2017_ca<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_ca") %>% 
  pull(ID)

 WM_2017_st<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_st") %>% 
  pull(ID)

 WM_2015_6<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_6") %>% 
  pull(ID)

 WM_2015_8<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_8") %>% 
  pull(ID)

 WM_2015_9<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_9") %>% 
  pull(ID)

 WM_2015_10<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_10") %>% 
  pull(ID)

 WM_2015_11<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_11") %>% 
  pull(ID)

 WM_2015_18<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_18") %>% 
  pull(ID)

 WM_2015_19<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_19") %>% 
  pull(ID)

 WM_2015_20<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_20") %>% 
  pull(ID)

 WM_2015_21<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_21") %>% 
  pull(ID)

 WM_2015_22<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_22") %>% 
  pull(ID)

 WM_2015_23<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_23") %>% 
  pull(ID)

 WM_2015_24<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_24") %>% 
  pull(ID)

 WM_2015_25<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_25") %>% 
  pull(ID)

 WM_2015_34<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_34") %>% 
  pull(ID)

 WM_2015_35<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_35") %>% 
  pull(ID)

 WM_2015_45<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_45") %>% 
  pull(ID)

 WM_2015_46<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_46") %>% 
  pull(ID)

 WM_2015_47<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_47") %>% 
  pull(ID)

 WM_2015_48<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_48") %>% 
  pull(ID)

 WM_2015_60<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_60") %>% 
  pull(ID)

 WM_2015_62<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_62") %>% 
  pull(ID)

 WM_2015_66<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_66") %>% 
  pull(ID)

WM_2015_67 <- WM3_ %>%
  filter(WM3_$Field_Names== "2015_67") %>% 
  pull(ID)

 WM_2015_68<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_68") %>% 
  pull(ID)

 WM_2015_69<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_69") %>% 
  pull(ID)

 WM_2015_75<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_75") %>% 
  pull(ID)

 WM_2015_78<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_78") %>% 
  pull(ID)

 WM_2015_97<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_97") %>% 
  pull(ID)

 WM_2015_98<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_98") %>% 
  pull(ID)

 WM_2015_99<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_99") %>% 
  pull(ID)

 WM_2015_100<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_100") %>% 
  pull(ID)

 WM_2015_101<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_101") %>% 
  pull(ID)

 WM_2015_102<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_102") %>% 
  pull(ID)

 WM_2015_103<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_103") %>% 
  pull(ID)

 WM_2015_104<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_104") %>% 
  pull(ID)

 WM_2015_Al<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_Al") %>% 
  pull(ID)

 WM_2015_Hi<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_Hi") %>% 
  pull(ID)

 WM_2015_In<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_In") %>% 
  pull(ID)

 WM_2015_mont<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_mont") %>% 
  pull(ID)

 WM_2015_Sand<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_Sand") %>% 
  pull(ID)

 WM_2015_Sani<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_Sani") %>% 
  pull(ID)

 WM_2015_St<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_St") %>% 
  pull(ID)

 WM_2015_wau<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_wau") %>% 
  pull(ID)

 WM_2015_la<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_la") %>% 
  pull(ID)

 WM_2015_co<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_co") %>% 
  pull(ID)

 WM_2015_cern<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_cern") %>% 
  pull(ID)

 WM_2015_cer<- WM3_ %>%
  filter(WM3_$Field_Names== "2015_cer") %>% 
  pull(ID)

 WM_2010<- WM3_ %>%
  filter(WM3_$Field_Names== "2010_") %>% 
  pull(ID)

 WM_2017<- WM3_ %>%
  filter(WM3_$Field_Names== "2017_") %>% 
  pull(ID)

###

  MI_East_Lansing <- WM3_ %>% 
  filter(WM3_$Field_Names== "lan") %>% 
  pull(ID)
IA_Nashua <- WM3_ %>% 
  filter(WM3_$Field_Names== "na") %>% 
  pull(ID)
WI_Hancock <- WM3_ %>% 
  filter(WM3_$Field_Names== "han") %>% 
  pull(ID)
MI_Montcalm_2017 <- WM3_ %>% 
  filter(WM3_$Field_Names== "mon") %>% 
  pull(ID)
MI_Montcalm_2015 <- WM3_ %>% 
  filter(WM3_$Field_Names== "mont") %>% 
  pull(ID)
WI_Cerny <- WM3_ %>% 
  filter(WM3_$Field_Names== "cer") %>% 
  pull(ID)

NE_Holt <- WM3_ %>% 
  filter(WM3_$Field_Names== "holt") %>% 
  pull(ID)

NE_Field_Names_34 <- WM3_ %>% 
  filter(WM3_$Field_Names== "34") %>% 
  pull(ID)

NE_Field_Names_67 <- WM3_ %>% 
  filter(WM3_$Field_Names== "67") %>% 
  pull(ID)

NE_Field_Names_75 <- WM3_ %>% 
  filter(WM3_$Field_Names== "75") %>% 
  pull(ID)

NE_Field_Names_97 <- WM3_ %>% 
  filter(WM3_$Field_Names== "97") %>% 
  pull(ID)

NE_Field_Names_98 <- WM3_ %>% 
  filter(WM3_$Field_Names== "98") %>% 
  pull(ID)

NE_Field_Names_101 <- WM3_ %>% 
  filter(WM3_$Field_Names== "101") %>% 
  pull(ID)

##
 MI_East_Lansing <- WM3_ %>% 
  filter(WM3_$Field== "lan") %>% 
  pull(ID)
IA_Nashua <- WM3_ %>% 
  filter(WM3_$Field== "na") %>% 
  pull(ID)
WI_Hancock <- WM3_ %>% 
  filter(WM3_$Field== "han") %>% 
  pull(ID)
MI_Montcalm_2017 <- WM3_ %>% 
  filter(WM3_$Field== "mon") %>% 
  pull(ID)
MI_Montcalm_2015 <- WM3_ %>% 
  filter(WM3_$Field== "mont") %>% 
  pull(ID)
WI_Cerny <- WM3_ %>% 
  filter(WM3_$Field== "cer") %>% 
  pull(ID)

NE_Holt <- WM3_ %>% 
  filter(WM3_$Field== "holt") %>% 
  pull(ID)
NE_Field_34 <- WM3_ %>% 
  filter(WM3_$Field== "34") %>% 
  pull(ID)

NE_Field_67 <- WM3_ %>% 
  filter(WM3_$Field== "67") %>% 
  pull(ID)

NE_Field_75 <- WM3_ %>% 
  filter(WM3_$Field== "75") %>% 
  pull(ID)

NE_Field_97 <- WM3_ %>% 
  filter(WM3_$Field== "97") %>% 
  pull(ID)

NE_Field_98 <- WM3_ %>% 
  filter(WM3_$Field== "98") %>% 
  pull(ID)

NE_Field_101 <- WM3_ %>% 
  filter(WM3_$Field== "101") %>% 
  pull(ID)

WM3_ <- WM3_ %>% 
   mutate(Year_Field= case_when(
ID %in%WM_1963~"1963",
ID %in%WM_1965~"1965",
ID %in%WM_1969~"1969",
ID %in%WM_1973~"1973",
ID %in%WM_1974~"1974",
ID %in%WM_1975~"1975",
ID %in%WM_1976~"1976",
ID %in%WM_1977~"1977",
ID %in%WM_1978~"1978",
ID %in%WM_1979~"1979",
ID %in%WM_1980~"1980",
ID %in%WM_1981~"1981",
ID %in%WM_1982~"1982",
ID %in%WM_1983~"1983",
ID %in%WM_1984~"1984",
ID %in%WM_1985~"1985",
ID %in%WM_1987~"1987",
ID %in%WM_1989~"1989",
ID %in%WM_1990~"1990",
ID %in%WM_1991~"1991",
ID %in%WM_1992~"1992",
ID %in%WM_1993~"1993",
ID %in%WM_1994~"1994",
ID %in%WM_1995~"1995",
ID %in%WM_1996~"1996",
ID %in%WM_1997~"1997",
ID %in%WM_1997_WM_production_31~"1997_production_31",
ID %in%WM_1997_WM_production_32~"1997_production_32",
ID %in%WM_1988~"1988",
ID %in%WM_1998~"1998",
ID %in%WM_1999~"1999",
ID %in%WM_2000~"2000",
ID %in%WM_2002~"2002",
ID %in%WM_2003~"2003",
ID %in%WM_1997_WM_production_33~"1997_production_33",
ID %in%WM_2003_WM_nursery_1~"2003_nursery_1",
ID %in%WM_2003_WM_nursery_2~"2003_nursery_2",
ID %in%WM_2003_WM_nursery_3~"2003_nursery_3",
ID %in%WM_1996_WM_nursery_4~"1996_nursery_4",
ID %in%WM_2003_WM_nursery_5~"2003_nursery_5",
ID %in%WM_2004~"2004",
ID %in%WM_2005~"2005",
ID %in%WM_2006~"2006",
ID %in%WM_2004_WM_nursery_6~"2004_nursery_6",
ID %in%WM_2004_WM_nursery_7~"2004_nursery_7",
ID %in%WM_2004_WM_nursery_8~"2004_nursery_8",
ID %in%WM_2004_WM_nursery_9~"2004_nursery_9",
ID %in%WM_2004_WM_nursery_10~"2004_nursery_10",
ID %in%WM_2004_WM_nursery_11~"2004_nursery_11",
ID %in%WM_2004_WM_nursery_12~"2004_nursery_12",
ID %in%WM_2005_WM_nursery_13~"2005_nursery_13",
ID %in%WM_2005_WM_nursery_14~"2005_nursery_14",
ID %in%WM_2005_WM_nursery_15~"2005_nursery_15",
ID %in%WM_2005_WM_nursery_16~"2005_nursery_16",
ID %in%WM_2005_WM_nursery_17~"2005_nursery_17",
ID %in%WM_2005_WM_nursery_18~"2005_nursery_18",
ID %in%WM_2006_WM_nursery_19~"2006_nursery_19",
ID %in%WM_2007~"2007",
ID %in%WM_2007_WM_production_1~"2007_production_1",
ID %in%WM_2007_WM_production_2~"2007_production_2",
ID %in%WM_2007_WM_production_3~"2007_production_3",
ID %in%WM_2007_WM_production_4~"2007_production_4",
ID %in%WM_2007_WM_production_5~"2007_production_5",
ID %in%WM_2007_WM_production_6~"2007_production_6",
ID %in%WM_2007_WM_production_7~"2007_production_7",
ID %in%WM_2007_WM_production_8~"2007_production_8",
ID %in%WM_2007_WM_production_9~"2007_production_9",
ID %in%WM_2008~"2008",
ID %in%WM_2008_WM_production_10~"2008_production_10",
ID %in%WM_2008_WM_nursery_20~"2008_nursery_20",
ID %in%WM_2008_WM_production_11~"2008_production_11",
ID %in%WM_2008_WM_production_12~"2008_production_12",
ID %in%WM_2008_WM_production_13~"2008_production_13",
ID %in%WM_2009~"2009",
ID %in%WM_2008_WM_nursery_21~"2008_nursery_21",
ID %in%WM_2009_WM_nursery_22~"2009_nursery_22",
ID %in%WM_2009_WM_nursery_23~"2009_nursery_23",
ID %in%WM_2009_WM_production_14~"2009_production_14",
ID %in%WM_2009_WM_production_15~"2009_production_15",
ID %in%WM_2009_WM_production_16~"2009_production_16",
ID %in%WM_2009_WM_production_17~"2009_production_17",
ID %in%WM_2009_WM_production_18~"2009_production_18",
ID %in%WM_2009_WM_production_19~"2009_production_19",
ID %in%WM_2009_WM_production_20~"2009_production_20",
ID %in%WM_2010_WM_production_21~"2010_production_21",
ID %in%WM_2010_WM_production_22~"2010_production_22",
ID %in%WM_2010_WM_production_23~"2010_production_23",
ID %in%WM_2010_WM_production_24~"2010_production_24",
ID %in%WM_2010_WM_production_25~"2010_production_25",
ID %in%WM_2010_WM_production_26~"2010_production_26",
ID %in%WM_2010_WM_production_27~"2010_production_27",
ID %in%WM_2010_WM_production_28~"2010_production_28",
ID %in%WM_2010_WM_production_29~"2010_production_29",
ID %in%WM_2010_WM_production_30~"2010_production_30",
ID %in%WM_2011~"2011",
ID %in%WM_2013~"2013",
ID %in%WM_2014~"2014",
ID %in%WM_2016~"2016",
ID %in%WM_2016_po~"2016_po",
ID %in%WM_2016_flo~"2016_flo",
ID %in%WM_2016_lan~"2016_lan",
ID %in%WM_2017_ho~"2017_ho",
ID %in%WM_2017_an~"2017_an",
ID %in%WM_2017_dod~"2017_dod",
ID %in%WM_2017_va~"2017_va",
ID %in%WM_2017_na~"2017_na",
ID %in%WM_2017_sa~"2017_sa",
ID %in%WM_2017_ha~"2017_ha",
ID %in%WM_2017_cu~"2017_cu",
ID %in%WM_2017_mon~"2017_mon",
ID %in%WM_2017_ant~"2017_ant",
ID %in%WM_2017_holt~"2017_holt",
ID %in%WM_2017_arr~"2017_arr",
ID %in%WM_2017_ini~"2017_ini",
ID %in%WM_2017_ley~"2017_ley",
ID %in%WM_2017_pre~"2017_pre",
ID %in%WM_2017_ru~"2017_ru",
ID %in%WM_2017_ca~"2017_ca",
ID %in%WM_2017_st~"2017_st",
ID %in%WM_2015_6~"2015_6",
ID %in%WM_2015_8~"2015_8",
ID %in%WM_2015_9~"2015_9",
ID %in%WM_2015_10~"2015_10",
ID %in%WM_2015_11~"2015_11",
ID %in%WM_2015_18~"2015_18",
ID %in%WM_2015_19~"2015_19",
ID %in%WM_2015_20~"2015_20",
ID %in%WM_2015_21~"2015_21",
ID %in%WM_2015_22~"2015_22",
ID %in%WM_2015_23~"2015_23",
ID %in%WM_2015_24~"2015_24",
ID %in%WM_2015_25~"2015_25",
ID %in%WM_2015_34~"2015_34",
ID %in%WM_2015_35~"2015_35",
ID %in%WM_2015_45~"2015_45",
ID %in%WM_2015_46~"2015_46",
ID %in%WM_2015_47~"2015_47",
ID %in%WM_2015_48~"2015_48",
ID %in%WM_2015_60~"2015_60",
ID %in%WM_2015_62~"2015_62",
ID %in%WM_2015_66~"2015_66",
ID %in%WM_2015_67~"2015_67",
ID %in%WM_2015_68~"2015_68",
ID %in%WM_2015_69~"2015_69",
ID %in%WM_2015_75~"2015_75",
ID %in%WM_2015_78~"2015_78",
ID %in%WM_2015_97~"2015_97",
ID %in%WM_2015_98~"2015_98",
ID %in%WM_2015_99~"2015_99",
ID %in%WM_2015_100~"2015_100",
ID %in%WM_2015_101~"2015_101",
ID %in%WM_2015_102~"2015_102",
ID %in%WM_2015_103~"2015_103",
ID %in%WM_2015_104~"2015_104",
ID %in%WM_2015_Al~"2015_Al",
ID %in%WM_2015_Hi~"2015_Hi",
ID %in%WM_2015_In~"2015_In",
ID %in%WM_2015_mont~"2015_mont",
ID %in%WM_2015_Sand~"2015_Sand",
ID %in%WM_2015_Sani~"2015_Sani",
ID %in%WM_2015_St~"2015_St",
ID %in%WM_2015_wau~"2015_wau",
ID %in%WM_2015_la~"2015_la",
ID %in%WM_2015_co~"2015_co",
ID %in%WM_2015_cern~"2015_cern",
ID %in%WM_2015_cer~"2015_cer",
ID %in%WM_2010~"2010",
ID %in%WM_2017~"2017",
TRUE ~ "no specific field"
),
State= case_when(
ID %in%WM_AB~"AB",
ID %in%WM_AZ~"AZ",
ID %in%WM_BA~"BA",
ID %in%WM_CA~"CA",
ID %in%WM_CO~"CO",
ID %in%WM_DE~"DE",
ID %in%WM_DF~"DF",
ID %in%WM_FL~"FL",
ID %in%WM_GA~"GA",
ID %in%WM_GO~"GO",

ID %in%WM_IA~"IA",
ID %in%WM_ID~"ID",
ID %in%WM_KS~"KS",
ID %in%WM_KY~"KY",
ID %in%WM_LA~"LA",
ID %in%WM_MD~"MD",
ID %in%WM_MG~"MG",
ID %in%WM_MI~"MI",
ID %in%WM_MN~"MN",
ID %in%WM_MO~"MO",

ID %in%WM_MS~"MS",
ID %in%WM_MT~"MT",
ID %in%WM_NC~"NC",
ID %in%WM_ND~"ND",
ID %in%WM_NE~"NE",
ID %in%WM_NY~"NY",
ID %in%WM_OH~"OH",
ID %in%WM_OK~"OK",
ID %in%WM_ON~"ON",
ID %in%WM_OR~"OR",

ID %in%WM_PA~"PA",
ID %in%WM_PR~"PR",
ID %in%WM_QUE~"QUE",
ID %in%WM_RS~"RS",
ID %in%WM_SC~"SC",
ID %in%WM_SIN~"SIN",
ID %in%WM_SK~"SK",
ID %in%WM_WI~"WI",
ID %in%WM_WA~"WA"

)
)%>% 
  mutate(Country = as.factor(Country),
         Year_Field = as.factor(Year_Field),
         State= as.factor(State)
         )



save(list = ls(all=TRUE), file= "all.Rdata")
 rm(list = ls())
```
# Collection
In 2016, and 2017, we conducted a survey of _S. sclerotiorum_ from soybean in NE, IA, WI, and MI, resulting in a collection of 1,369 isolates, which included farmer fields and fungicide field trials. In 2003 to 2012, 366 isolates were collected and characterized previously from white mold screening nurseries or producer fields throughout dry bean and snap bean production areas across the US, with others collected in prior years.  

From these, we randomly selected 207 isolates: 93 from dry beans (18 ND, 16 MI, 16 WA, 15 CO, 11 NE, 2 DE, 2 MN, 2 WI, 1 OR, 6 from Brazil and, 4 from Mexico) and 114 from soybeans (48 NE, 25 MI, 24 IA, and 17 WI). Isolates were from farmer fields (FF), fungicide field trials (FFT), and fields without fungicide applications, that latter were called baseline.

# Fungicides
## Boscalid
## Picoxystrobin
## Tetraconazole
## Thiophanate methyl

#  Fungicide sensitivity by fungicide
## Serial dilution
Fungicide sensitivity was determined since 21 baseline isolates plus 21 additional isolates from FF and FFT randomly selected. Serial dilution  by fungicide eas carried out from 5-6 concentrations with 4 repetitions per isolate and 2 experimental replications. Plates were incubated in darkness at 23  2 C for 42 h and diameter measured with digital calipers. A dose-response curve was fit to estimate the EC50 for each fungicide.  

## Procedure to get the Discriminatory Concentration (DC)  

We identified the concentration with the best prediction of EC50 for each fungicide, known as discriminatory concentration (DC), by linear regression of % mycelial growth vs. log(EC50). The concentration yielding the highest coefficient of determination (r2) was selected as the DC for each fungicide. For the remaining isolates among the 207, growth on the DC was used to estimate EC50, which is termed EC50(D).

##  Use of the Discriminatory Concentration DC

We randomly selected 154 isolates: 86 from dry beans (from 9 states with 1-17 isolates/state, and 2 states from Brazil) and 66 from soybeans (6 NE, 18 IA, 13 WI & 18 MI and 4 from Mexico)  from the collection (baseline, FF, and FF) plus 5 same isolates used in the serial dilution approach

